---
title: "Excel-Style Hexavigesimal (A to Z)"
author: Tingting Zhan
format: 
  html:
    page-layout: full
    html-math-method: katex
toc: true
toc-location: left
toc-depth: 4
toc-title: ''
editor: source
knitr:
  opts_chunk: 
    collapse: true
    comment: "#" 
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette of package **`hexExcel`** ([Github](https://github.com/tingtingzhan/hexExcel), [RPubs](https://rpubs.com/tingtingzhan/hexExcel)) documents ...

## Prerequisite

New features are first implemented on [Github](https://github.com/tingtingzhan/TukeyGH77).

```{r}
#| warning: false
#| eval: false
remotes::install_github('tingtingzhan/hexExcel')
```

## Note to Users

Examples in this vignette require that the `search` path has

```{r}
library(hexExcel)
```

```{r}
#| echo: false
#options(mc.cores = 1L) # for CRAN submission
```

# Conversion Table

Convert between decimal `integer`, C-style hexavigesimal `0-9, A-P`, and Excel-style hexavigesimal `A-Z`.

```{r}
int = c(NA_integer_, 1L, 9L, 10L, 25L, 26L, 27L, 51L, 52L, 676L, 702L, 703L)
hex_Excel = int |> int2Excel()
```

```{r}
#| code-fold: true
#| code-summary: 'R code: to create this table'
#| results: asis
c(
  'Hexavigesimal, Excel-Style', paste0('`', hex_Excel, '`'),
  'Hexavigesimal, C-Style', paste0('`', hex_Excel |> Excel2C() |> toupper(), '`')
) |>
  matrix(ncol = 2L, dimnames = list(c('Decimal `integer` to Hexavigesimal', as.character(int)), NULL)) |>
  t.default() |>
  as.data.frame.matrix() |> 
  knitr::kable() 
```

## `Excel2C()`

Function `Excel2C()` converts Excel-style hexavigesimal `A-Z` to C-style hexavigesimal `0-9, A-P`.

```{r}
hex_Excel |>
  Excel2C()
```

## `Excel2int()`

Function `Excel2int()` converts Excel-style hexavigesimal `A-Z` to decimal `integer`, using function `Excel2C()` and `base::strtoi()`.

```{r}
hex_Excel |>
  Excel2int()
```

## `int2Excel()`

Function `int2Excel()` converts decimal `integer` to Excel-style hexavigesimal `A-Z`.

```{r}
int |> 
  int2Excel()
```

Function `int2Excel()` works very differently from R's solution to hexadecimal and decimal conversions. Function `base::as.hexmode()` returns an object of `typeof` `integer`. Then, function `base::format.hexmode()`, i.e., the workhorse of function `base::print.hexmode()`, relies on the `%x` (hexadecimal) format option of function `base::sprintf()`.


# Appendix

## Terms & Abbreviations

| Term / Abbreviation | Description |
|------------------------------------|------------------------------------|
| [`|>`](https://search.r-project.org/R/refmans/base/html/pipeOp.html) | Forward pipe operator introduced since R 4.1.0 |
| `$` | [Extract](https://search.r-project.org/R/refmans/base/html/Extract.html) parts of an object |
| CRAN, R | [The Comprehensive R Archive Network](https://cran.r-project.org) |
| [`class`](https://search.r-project.org/R/refmans/base/html/class.html) | Object class |
| hexadecimal, [`as.hexmode`](https://search.r-project.org/R/refmans/base/html/hexmode.html) | Base-16 number system |
| hexavigesimal | Base-26 number system, in [C-style](https://mathworld.wolfram.com/Hexavigesimal.html) |
| `S3`, `generic`, [`methods`](https://search.r-project.org/R/refmans/utils/html/methods.html) | `S3` object oriented system, [`UseMethod`](https://search.r-project.org/R/refmans/base/html/UseMethod.html); [`getS3method`](https://search.r-project.org/R/refmans/utils/html/getS3method.html); <https://adv-r.hadley.nz/s3.html> |
| `S4`, `generic`, `methods` | `S4` object oriented system, [`isS4`](https://search.r-project.org/R/refmans/base/html/isS4.html); [`setClass`](https://search.r-project.org/R/refmans/methods/html/setClass.html); [`getMethod`](https://search.r-project.org/R/refmans/methods/html/getMethod.html); <https://adv-r.hadley.nz/s4.html> |
| [`search`](https://search.r-project.org/R/refmans/base/html/search.html) | Search path |

